\documentclass[man,floatsintext,biblatex,a4paper]{apa7}
%\usepackage[author={Marten de Vries},color=yellow,open=true]{pdfcomment}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pdflscape}

%- check discussion
%- check layout
%- check all
%- fix LaTeX errors
%- check references?

\addbibresource{literature.bib}

\title{Measuring Inter-Brain Synchrony: Methods and Pitfalls}
\shorttitle{Measuring Inter-Brain Synchrony: Methods and Pitfalls}

\leftheader{de Vries}
\author{Marten de Vries\\~}
\authorsaffiliations{Graduation Project\\
Computational Cognitive Science\\
University of Groningen\\~\\
Supervisors: Dr. Marieke van Vugt \& Lionel Newman MSc}
\date{December 2022}

\abstract{
Collecting EEG data for two participants simultaneously during a task (i.e.,
hyperscanning) allows us to study their social interaction. Of particular
interest is their inter-brain synchrony (IBS), i.e. how functionally similar
their neural oscillations are. Using a full IBS analysis of a tacit coordination
experiment and simulations, we study the effect of different methodological
choices in an IBS measurement pipeline. Three ways to quantify IBS are studied:
the phase-locking value (PLV), the circular correlation (CCorr) and the
imaginary part of coherency (ImagCoh). Each measures functional similarity in
its own way and has its advantages and disadvantages. We find the CCorr measure
to be less stable than the others, but still recommend its use along with the
PLV measure because of its natural interpretation and good performance
on simulated data. We present a robust version of the circular correlation
measure and make recommendations for how to best perform an IBS analysis.}

\keywords{Hyperscanning, Inter-Brain Synchrony, methodology, simulation, Tacit
Coordination, Theory of Mind, phase locking value, circular correlation,
imaginary part of coherency}

\begin{document}
\maketitle
\tableofcontents\newpage

\input{introduction}
\input{methods}
\input{simulation}
\input{freqanalysis}
\input{permutationtest}
\input{timecourse}
\input{prediction}
\input{discussion}
\input{appendices}
\printbibliography
\end{document}
